---
title: "Social Network Analysis Project: Ant colony network analysis"
output: html_notebook
---

```{r}
source("utils.R")
path <- '../Files'

graphList <- create_graphs(path, columns = c("v1","v2","weight"))
graphs <- list(graphList[[1]],graphList[[20]],graphList[[41]])
gstat0 <- graph_stats(graphs)
summary(gstat0)
```

```{r}
gwgt <- to_list(for (g in graphs) E(g)$weight)
```
```{r}
summary(gwgt[[1]])
```

```{r}
plot(graphs[[1]]-E(graphs[[1]])[weight < 2], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```

```{r}
summary(gwgt[[2]])
```
```{r}
plot(graphs[[2]]-E(graphs[[2]])[weight < 2], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```

```{r}
summary(gwgt[[3]])
```

```{r}
plot(graphs[[3]]-E(graphs[[3]])[weight < 2 ], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```
# As we can see the most of the weights is below 10 while the maximum weights is  between 73 and 134 which make a lot of edges have weights less that the mean, with fewer greater than the mean; let's visualize the 1st graph and last graph

# Calculating triad subgraphs and their weights for the first and the last graphs
```{r}
triad_subs1 <- triad_cli(graphList[[1]])
triad_subs20 <- triad_cli(graphList[[20]])
triad_subs41 <- triad_cli(graphList[[41]])
```

```{r}
# Calculating the weights for the 1st the middle and the last graph's sub graphs
weights1 <- to_vec(for (t in triad_subs1) sub_weights(graphList[[1]], t))
summary(weights1)
```

```{r}
# Calculating the weights for the 1st the middle and the last graph's sub graphs
weights20 <- to_vec(for (t in triad_subs20) sub_weights(graphList[[20]], t))
summary(weights20)
```

```{r}
# Calculating the weights for the 1st the middle and the last graph's sub graphs
weights41 <- to_vec(for (t in triad_subs41) sub_weights(graphList[[41]], t))
summary(weights41)
```

# Creating random graphs for each graph
```{r}
# Random graphs
nm <- to_list(for (g in graphs) nulmodel(g))
Rtriads <- to_list(for (g in nm) triad_cli(g))
# Graphs statistics
gstat <- graph_stats(nm)
Rwgt <- to_vec(for (g in nm) E(g)$weight)
summary(gstat)
```

```{r}
summary(Rwgt[[1]])
```
```{r}
plot(nm[[1]]-E(nm[[1]])[weight < 36], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```
```{r}
summary(Rwgt[[2]])
```
```{r}
plot(nm[[2]]-E(nm[[2]])[weight < 43], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```
```{r}
summary(Rwgt[[3]])
```
```{r}
plot(nm[[3]]-E(nm[[3]])[weight < 115], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```
```{r}
# Random graphs
nm2 <- to_list(for (g in graphs) nulmodel(g))
Rtriads2 <- to_list(for (g in nm2) triad_cli(g))
# Graphs statistics
gstat2 <- graph_stats(nm2)
Rwgt2 <- to_vec(for (g in nm2) E(g)$weight)
summary(gstat2)
```


```{r}
summary(Rwgt2[[1]])
```
```{r}
plot(nm2[[1]]-E(nm2[[1]])[weight < 124], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```

```{r}
summary(Rwgt2[[2]])
```
```{r}
plot(nm2[[2]]-E(nm2[[2]])[weight < 124], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```

```{r}
summary(Rwgt2[[3]])
```
```{r}
plot(nm2[[3]]-E(nm2[[3]])[weight < 110], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```


```{r}
# Random graphs
nm3 <- to_list(for (g in graphs) nulmodel(g))
Rtriads3 <- to_list(for (g in nm3) triad_cli(g))
# Graphs stats
gstat3 <- graph_stats(nm3)
Rgwt3 <- to_vec(for (g in nm3) E(g)$weight)
summary(gstat3)
```

```{r}
summary(Rgwt3[[1]])
```
```{r}
plot(nm3[[1]]-E(nm3[[1]])[weight < 77], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```

```{r}
summary(Rgwt3[[2]])
```
```{r}
plot(nm3[[2]]-E(nm3[[2]])[weight < 11], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```
```{r}
summary(Rgwt3[[3]])
```
```{r}
plot(nm3[[3]]-E(nm3[[3]])[weight < 11], vertex.label=NA, vertex.size=5, edge.curved=T, layout=layout_with_fr)
```


# As we can see the degree distribution doesn't change with the randomized graph, that's because       
# they're were built in a manner to keep that property for all the random graphs, while it just change 
# the interactions between the nodes.
# Normally it is required to create more than 3 random models but it requires a big computational power 
# to calculate triad subgraphs and their weights so we're just limiting ourselves to just 3 random     
# models and we will calculate the weights for just some graphs which seem to be important

```{r}
Rweights1 <- to_vec(for (t in Rtriads[[1]]) sub_weights(nm[[1]], t))
summary(Rweights1)
```

```{r}
Rweights20 <- to_vec(for (t in Rtriads[[2]]) sub_weights(nm[[2]], t))
summary(Rweights20)
```

```{r}
Rweights3 <- to_vec(for (t in Rtriads[[3]]) sub_weights(nm[[3]], t))
summary(Rweights3)
```

```{r}
R2weights1 <- to_vec(for (t in Rtriads2[[1]]) sub_weights(nm2[[1]], t))
summary(R2weights1)
```

```{r}
R2weights2 <- to_vec(for (t in Rtriads2[[2]]) sub_weights(nm2[[2]], t))
summary(R2weights2)
```

```{r}
R2weights3 <- to_vec(for (t in Rtriads2[[3]]) sub_weights(nm2[[3]], t))
summary(R2weights3)
```


```{r}
R3weights1 <- to_vec(for (t in Rtriads3[[1]]) sub_weights(nm[[1]], t))
summary(R3weights1)
```

```{r}
R3weights2 <- to_vec(for (t in Rtriads3[[2]]) sub_weights(nm[[2]], t))
summary(R3weights2)
```

```{r}
R3weights3 <- to_vec(for (t in Rtriads3[[3]]) sub_weights(nm[[3]], t))
summary(R3weights3)
```
